Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-04-23 main.Rmd
proof read changes

Consider a linear granularity $G'$ such that $G' = Alter^{2}_{(1,-2)}(B, Group_7(B))$, which implies it is made up of shrinking every 1st granule of $Group_7(B)$ by $2$ granules.<!-- $$G'= Alter^{2}_{(1,-1)}(BG, Group_3(B))$$ and --><!--This implies that $G'$ is made up by shrinking every 1st granule of $Group_3(B)$ by $1$ granule and $H'$ is made up of shrinking every 1st granule of $Group_3(B)$ by $2$ granules. Number of granules of $G'$ and $H'$ in each period of $B$ is 2 but the number of granules of $B$ in each of those granules are different.--> Then $Q_{B, G'}$ is a repetitive categorization of time, similar to circular granularities, except that the number of granules of $B$ is not necessarily the same across different granules of $G'$. Here, $T_0 = \{0, 1, 2, 3, 4, 5, 6\}$ and $T_1 = \{7, 8, 9, 10, 11\}$. Hence using Defintion \autoref{def:quasicircular} we will have:

@@

From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. Recalling the data structure <$C1$, $C2$, `general_supply_kwh`> that we would use for exploration, each of these six cyclic granularities can either be mapped to x-axis or to facet. Thus the problem is equivalent to choosing 2 granularities at a time from 6, which essentially is equivalent to having 30 data subsets for visualization. However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting pairs together. \autoref{tab:harmony-tab} shows 13 harmonies pairs with any cyclic granularities with levels more than 31 removed as effective exploration becomes difficult with many levels (Section \ref{sec:levels}). For each of \autoref{fig:bothcust} (b) and (c), $C1$ is the circular granularity day-type (weekday/ weekend) and $C2$ is hour of the day. The geometry used for displaying the distribution is chosen as area-quantiles \autoref{fig:bothcust} (b) and violins for \autoref{fig:bothcust} (b). \autoref{fig:bothcust} (a) displays reverse mapping of $C1$ and $C2$ with $C1$ now denoting hour of the day and $C2$ denoting day-type and geometry for displaying distribution is boxplots.

>>>>

Consider a linear granularity $G'$ such that $G' = Alter^{2}_{(1,-2)}(B, Group_7(B))$, which implies it is made up of shrinking every 1st granule of $Group_7(B)$ by $2$ granules.<!-- $$G'= Alter^{2}_{(1,-1)}(BG, Group_3(B))$$ and --><!--This implies that $G'$ is made up by shrinking every 1st granule of $Group_3(B)$ by $1$ granule and $H'$ is made up of shrinking every 1st granule of $Group_3(B)$ by $2$ granules. Number of granules of $G'$ and $H'$ in each period of $B$ is 2 but the number of granules of $B$ in each of those granules are different.--> Then $Q_{B, G'}$ is a repetitive categorization of time, similar to circular granularities, except that the number of granules of $B$ is not necessarily the same across different granules of $G'$. Here, $T_0 = \{0, 1, 2, 3, 4, 5, 6\}$ and $T_1 = \{7, 8, 9, 10, 11\}$. Hence using Definition \autoref{def:quasicircular} we will have:

@@

From the search list, we found six cyclic granularities for which we would like to derive insights of energy behavior. Recalling the data structure <$C1$, $C2$, `general_supply_kwh`> that we would use for exploration, each of these six cyclic granularities can either be mapped to x-axis or to facet. Thus the problem is equivalent to choosing 2 granularities at a time from 6, which essentially is equivalent to having 30 data subsets for visualization. However, harmony/clash pairs can be identified among those 30 possibilities to determine feasibility of plotting pairs together. \autoref{tab:harmony-tab} shows 13 harmonies pairs with any cyclic granularities with levels more than 31 removed as effective exploration becomes difficult with many levels (Section \ref{sec:levels}). For each of \autoref{fig:bothcust} (b) and (c), $C1$ is the circular granularity day-type (weekday/ weekend) and $C2$ is hour of the day. The geometry used for displaying the distribution is chosen as area-quantiles.  \autoref{fig:bothcust} (b) and violins for \autoref{fig:bothcust} (b). \autoref{fig:bothcust} (a) displays reverse mapping of $C1$ and $C2$ with $C1$ now denoting hour of the day and $C2$ denoting day-type and geometry for displaying distribution is boxplots.
